\documentclass[a4paper, 11pt]{article}

\begin{document}
%Header-Make sure you update this information!!!!
\noindent
\large\textbf{Obligatory Assignment 1 Report} \hfill \textbf{Tomasz Gliniecki} \\

\section*{Problem Statement}
\subsection*{Monty Hall problem}
When a contestant is to choose on of three gates, which behind one of them is a prize, one can choose strategy as a result of the rules of the game. After the initial choice of the gate one ot the remaining gates that \emph{has no car behind it} gets reveiled. Now the strategy is either to keep the initial gate or switch.\\
The most effective strategy \emph{in the long run} is to ALWAYS SWITCH. This is because, one has always 2/3 chance of winning by swithcing. This is obvoius because, there is 1/3 chance of finding the prize which is behind 1 of the 3 gates, that means that there is 2/3 chance of NOT finding the prize. If we set our goal to NOT find the prize, and then switch when the empty gate opens, we will win with a 2/3 probability, because there is 2/3 chance of not finding the prize!

\subsection*{Rock Paper Scissors}


\section*{Solutions}


\section*{Construction/Implementation}

\section*{Attachments}
%Make sure to change these
Lab Notes, HelloWorld.ic, FooBar.ic
%\fi %comment me out

\begin{thebibliography}{9}
  
\bibitem{montyhall} 
  
\bibitem{rps}  Flueck, Alexander J. 2005. \emph{ECE 100}[online]. Chicago: Illinois Institute of Technology, Electrical and Computer Engineering Department, 2005 [cited 30
  August 2005]. Available from World Wide Web: (http://www.ece.iit.edu/~flueck/ece100).

\end{thebibliography}

\end{document}
